
```{r, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(message = FALSE)
options(mrgsolve.soloc = "build")
```


```{r, include = FALSE}
source("../global.R")
library(mrgsolve)
library(tidyverse)
library(knitr)
library(lattice)

```

```{r setup, echo = FALSE, message = FALSE}
mod <- mread_cache("pk1", modlib()) %>% 
  update(end = 192, delta = 0.2) %>% Req(CP)
data(exidata)
data <- filter(exidata, ID <= 10)
set.seed(1222)
```

# Pharmacokinetics

```{r, echo = FALSE}
mod %>% ev(amt = 100) %>% mrgsim(end = 72) %>% plot()
```

* Compartmental models
* Models with analytical solutions


# Dosing regimens

```{r, echo = FALSE}
mod %>% ev(amt = 100, ii = 24, addl = 4) %>% mrgsim() %>% plot()
```

# Dosing regimens

```{r, echo = FALSE}
e1 <- ev(amt = 100, ii = 24, addl = 9)
e2 <- ev(amt = 50, ii = 12, addl = 19)
e <- seq(e1,e2,e1)
mod %>% ev(e) %>% mrgsim(end=248*3+96) %>% plot()
```



# Population simulation

```{r, echo = FALSE, message=FALSE}
mod <- mread_cache("popex", modlib()) %>% Req(DV)
data <- expand.ev(amt = 300, ii = 24, addl = 4, ID = seq(20))
mod %>% data_set(data) %>% mrgsim() %>% plot()
```

# PKPD

```{r, echo = FALSE}
omod <- mread("opg", "../../model") %>%  update(end = 24*14) %>% zero_re(sigma)
# 
odat <- ev(amt = 210) %>% ev_rep(ID = seq(100))
out <- mrgsim(omod, data = odat) %>% mutate_sims(week=time/24/7)
plot(out,PKDV+dNTX ~ week)

out %>% as_tibble() %>% filter(week==2) %>% summarise(Median_CFB = median(dNTX))
```

# Sensitivity analysis

```{r, echo = FALSE}
idata <- tibble(VC = c(20,60,180))
hmod <- mrgsolve:::house() %>% Req(DV,RESP) %>% update(end = 244)
hmod %>% mrgsim(idata = idata,  end = 24*28, delta = 0.1,
                events = ev(amt = 100, ii = 24, addl = 28)) %>%
  plot(DV~.)
```


# Mechanistic models

```{r, echo = FALSE}
mod <- mread_cache("conway", "../../model")
e <- ev(amt = 1, evid = 8, time = 180) + ev(amt = 0, evid = 8, time = 2.5*365)
idata <- tibble(L_0 = c(1,3,5,7,10))
out <- mrgsim(mod, events = e, idata = idata, end = 6*365, delta = 1)
out@data <- mutate(out@data, time = time - 180)
plot(out, logV+L~(time/365), xlab = "Time (year)")
```


# About `mrgsolve` 

- `R` package for simulation from ODE-based models
    - Free, OpenSource, GitHub, CRAN
- Language
    - Models written in `C++` inside model specification format
    - General purpose solver: `ODEPACK` / `DLSODA` (`FORTRAN`)
        - Automatically detect and switch between non-stiff (Adams) and stiff (BDF)
          methods for solving the differential equations
    - Simulation workflow in `R`
- Hierarchical (population) simulation
    - `ID`, $\eta$, $\varepsilon$
- Integrated PK functionaility
    - Bolus, infusion, `F`, `ALAG`, `SS` etc, handled under the hood
    - 1- and 2-cmt PK models in closed-form
- Extensible using `R`, `C++`, `Rcpp`, `boost`, `RcppArmadillo`
- `R` is it's natural habitat

# `mrgsolve` started as `QSP` modeling tool
- Motivation: large bone/mineral homeostatsis model (CaBone)
- History using
    - Berkeley Madonna
    - WinBUGS
    - NONMEM (attempted)
- 2010: write `R` front end to `deSolve`
- 2012: write `C++` interface to `DLSODA`
- Develop dosing / event capability
- More recently, expose functionality provided by
    - `Rcpp` - vectors, matrices, functions, environments, random numbers 
    - `boost` - numerical tools in `C++`
    - users' own `C++` code (functions, data structures, classes)
- Translator from `SBML` to `mrgsolve` using `R` bindings to `libSBML`   


# Orientation

- https://CRAN.R-project.org/package=mrgsolve

- GitHub site: https://github.com/metrumresearchgroup/mrgsolve

- Issues and questions: https://github.com/metrumresearchgroup/mrgsolve/issues

- mrgsolve website: https://mrgsolve.github.io

- User Guide: https://mrgsolve.github.io/user_guide

- Blog: https://mrgsolve.github.io/blog

- Vignettes: https://mrgsolve.github.io/vignettes

# What we will cover today

1. Three basic workflows
1. Loading the model into R
1. Event objects
1. Data sets

<h3><grn>Emphasis is on getting you running your own simulations today.</grn></h3>
