

```{r, include = FALSE}
source("../global.R")
library(mrgsolve)
library(dplyr)
library(knitr)
library(lattice)
```

```{r setup-1, echo = FALSE, message = FALSE}
mod <- mread_cache("pk1", modlib()) %>% 
  update(end = 192, delta = 0.2) %>% Req(CP)
data(exidata)
data <- filter(exidata, ID <=10)
set.seed(1222)
```

# A basic simulation with mrgsolve
```{r}
mod %>% ev(amt = 100, ii = 24, addl = 3) %>% mrgsim() %>% plot()
```

The first / simplest workflow. 

# A basic simulation with mrgsolve

```{r, eval = FALSE}
mod %>% ev(amt = 100, ii = 24, addl = 3) %>% mrgsim() %>% plot()
```

- <red>mod</red>: the model object
    - Ok ... where did `that` come from?
- <blu>ev(amt = 100, ...)</blu> : the intervention
    - An `event` in this example
- <grn>mrgsim()</grn>: actually do the simulation
- <orng>plot()</orng>: do something with the simulation
    - `plot`, `mutate`, `as_data_frame` etc ... 


> - <red>model</red> `%>%` <blu>intervention</blu> `%>%` <grn>simulate</grn> `%>%` <orng>take-a-look</orng> 

<!-- # What's coming ... -->

<!-- > - `model %>% intervention %>%` <alrt>options</alrt> `%>% simulate %>% ...` -->

<!-- > - `model %>% intervention %>%` <orng>population</orng> `%>% simulate %>% ...` -->

<!-- > - `model %>%` <purp>data-set</purp> `%>% simulate %>% ...` -->

<!-- > - where <purp>data-set</purp> = `intervention + population` -->

<!-- > - For now, let's get this part down  -->

<!-- > - <red>model</red> `%>%` <blu>intervention</blu> `%>%` <grn>simulate</grn> `%>%` <orng>take-a-look<orng>  -->


# Why do we use `%>%` ?

What happens first in this operation?

```{r, eval = FALSE}
mean(sqrt(seq(4)))
```

# Pipelines

```{r, eval = FALSE}
mean(sqrt(seq(4)))
```

```{r, eval = FALSE}
4  %>% seq() %>% sqrt() %>% mean()
```

Better.

```{r, eval = FALSE}
4  %>% 
  seq(.) %>% 
  sqrt(.) %>% 
  mean(., na.rm = TRUE)
```

```{r,eval = FALSE}
mod %>% some_intervention() %>% simulate() %>% post_process()
```


# The model object

<red>mod</red><blk>el</blk> `%>% ... `

> - I (almost) always call the model object <red>mod</red> in the documention / examples

> - All the information about the model we need to know to run the simulation

> - <grn>Distinct</grn> from the intervention, the population, the summary

> - But the model <orng>does</orng> know  about output time, random effects


# Take a look: overview

```{r, comment = ""}
mod
```

# Take a look: parameters (<red>really important</red>)
```{r, comment = ""}
param(mod)
```

> - Parameters get a name
> - Names and number of parameters gets fixed at compile time
> - All parameters have a value
> - Value can be modified after compile time

# Any advanced simulation will need to manipulate the model parameters in some way or another

- Can be `CL`, `V2`, `Q` etc 
- Fixed effect parameter estimates (`THETA`s)
- Covariates (`WT`, `EGFR` etc)
- Flags
  - Is the dosing weight-based or flat?  You could make a flag for that.

# Take a look: compartments
```{r, comment = ""}
init(mod)
```

> - Every compartment gets a name
> - Every compartment gets an initial condition
