
```{r, include = FALSE}
source("../global.R")
library(mrgsolve)
library(dplyr)
library(knitr)
library(lattice)
```

```{r echo = FALSE, message = FALSE}
mod <- mread_cache("pk1", modlib()) %>% 
  update(end = 192, delta = 0.2) %>% Req(CP)
data(exidata)
data <- filter(exidata, ID <=10)
set.seed(1222)
```

# Where did <red>mod</red> come from?

```{r,eval = FALSE}
mod <- mread("simple", "../../model")
```


```{r, eval = FALSE}
mod <- mread("<model-name>", "<project-directory>")
```

- By default mrgsolve looks for the code in the file
    - <grn>model-name.cpp</grn> in
    - <blu>project-directory</blu>

- <red>mread demo</red>

```{r, echo = FALSE}
Sys.sleep(2)
```



# Internal model library

Quiz:

```{r, eval = FALSE}
mod <- mread("<first-argument>", "<second-argument>")
```

# Internal model library

Quiz:

```{r, eval = FALSE}
mod <- mread("<first-argument>", "<second-argument>")
```

```{r, eval = FALSE}
mod <- mread("<first-argument>", modlib())
```

```{r}
modlib()
```


# Internal model library
```{r}
mod <- mread("effect", modlib())
```

```{r}
mod
```



# Try this now

```{r,eval=FALSE}
mod <- mread("pbpk", modlib())
```


```{r}
mod <- modlib("pbpk")
```

# Oops 
```{r}
mod <- try(mread("simple"))

mod
```

# <red>Your turn</red>

Summary: 

* Use `mread` to read, compile and load a model
* We can get information out of the model object that was returned
* This is the first step to get simulating (need a model first!)
* We will cover _writing_ the model later on

<BR>

- File name: <grn>exercises/warm_up.R</grn>


