
```{r, include = FALSE}
source("../global.R")
library(mrgsolve)
library(dplyr)
library(knitr)
library(lattice)
library(tidyverse)
select <- dplyr::select
```


# Sensitivity analysis

- Ad-hoc
  - Sequential: systematically vary the parameter value
  - Random: sample from a parametric or non-parametric distribution
- Local
    - small changes around a nominal value; one at a time
- Global
    - explore the whole parameter space; includes interactions


# Local sensitivity analysis - `sensFun()`

We use the function `sensFun` from the package FME (`FME::sensFun`)

```{r}
library(FME)
```


```{r, eval = FALSE}
?sensFun
```

- To do local sensitivity analysis, we need 
    - A function that accepts parameters as an argument and 
      returns simulated data
    - Some parameters to test
    - An output variable of interest

```{r, eval=FALSE}
sens <- sensFun(my_function, my_parameters, sensvar = my_variable_name)
```

- `sensFun` will take the parameter values we passed and manipulate them by 
  small amounts to determine the __local__ sensitivity

# First, look at the result


```{r, echo = FALSE,fig.align="center", fig.height = 8, fig.width = 12}
myfun <- function(pars, mod) {
  mod %>% 
    param(pars) %>% 
    ev(amt = 100) %>% 
    Req(CP,RESP) %>%
    mrgsim(end = 72) %>%
    as.data.frame %>% 
    select(-ID)
}
mod <- modlib("irm1", end = 72, delta = 0.1)
sims <- mod %>% ev(amt = 100) %>% mrgsim() %>% mutate(var="Concentration",variable="CP",value=CP)
sims <- select(sims, time,CP,var,variable,value)
sens <- sensFun(myfun, parms=param(mod)[c("CL", "V2", "Q", "V3", "KA")],mod=mod,sensvar="CP")
df <- gather(sens,variable,value, CL:KA) %>% mutate(time = x, var = "Sensitivity")
df <- bind_rows(df,sims)               
ggplot(df, aes(time,value,col=variable)) + geom_line(lwd=1) + 
  facet_wrap(~var, scales = "free_y") + theme_bw() + theme(legend.position="top")
```




# A simulation scenario of interest

```{r}
mod <- modlib("irm1", end = 72, delta = 0.1)

mod %>%
  ev(amt = 100) %>% 
  mrgsim(end = 72, delta = 0.1) %>% 
  plot
```


# Create `myfun` to capture the scenario

- This is the same workflow, but we wrap it in a function and allow
parameters (and the model) to be passed in as arguments

```{r}

myfun <- function(pars, mod) {
  mod %>% 
    param(pars) %>% 
    ev(amt = 100) %>% 
    mrgsim(end = 72) %>%
    as.data.frame %>% 
    select(-ID)
}
```

- Also, we don't plot the result, but rather return a data frame 


# Test out `myfun`
```{r}
myfun(param(mod), mod) %>% head()
```

# Pick some parameters
```{r}
pars <- param(mod)[c("CL", "V2", "V3", "KA")]

pars
```


# Run the analysis
```{r}
sens <- sensFun(myfun, pars, sensvar = "CP", mod = mod)

head(sens, n=3)
```

# The default plot method
```{r}
plot(sens, legpos = "right")

```

# Re-shape sensitivity analysis results
```{r}
sens %>% 
  gather(variable,value,CL:KA) %>% 
  ggplot(aes(x,value,col=variable)) + geom_line(lwd=1) + theme_bw()

```

# Global senstivity analysis

- All the parameters vary at once
- Investigate the whole parameter space
    - Or reasonable parameter space
- Evaluate both individual parameters as well as interactions between parameters
- Much greater computational burden


__We'll look at Sobol's method__


# Global senstivity analysis


- __Sobol Sensitivity Analysis: A Tool to Guide the Development and Evaluation of 
Systems Pharmacology Models.__
    - Zhang XY, Trame MN, Lesko LJ, Schmidt S.
    - CPT Pharmacometrics Syst Pharmacol. 2015 Feb;4(2):69-79. doi: 10.1002/psp4.6.
    - PMID: 27548289 
    - https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5006244/

# Global senstivity analysis


- __Sobol Sensitivity Analysis: A Tool to Guide the Development and Evaluation of 
~~Systems Pharmacology~~ PBPK Models.__
    - Zhang XY, Trame MN, Lesko LJ, Schmidt S.
    - CPT Pharmacometrics Syst Pharmacol. 2015 Feb;4(2):69-79. doi: 10.1002/psp4.6.
    - PMID: 27548289 
    - https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5006244/

# Sobol

- Variabillity in the output is decomposed, relating to variability in 
  different inputs or combinations of inputs

