
```{r, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(message = FALSE)
options(mrgsolve.soloc = "build")
```


```{r, include = FALSE}
source("../global.R")
library(mrgsolve)
library(dplyr)
library(knitr)
library(lattice)
```

# Case study: ciprofloxacin PBPK

- fluoroquinolone antibiotic
    - UTI , uncomplicated cystitis, SSTI, respiratory tract infection
    - Pseudomonas aeroginosa
    - [Bacillus anthracis](https://www.fda.gov/Drugs/EmergencyPreparedness/BioterrorismandDrugPreparedness/ucm063485.htm)
- PBPK model
    - A whole-body physiologically based pharmacokinetic (WB-PBPK) model of ciprofloxacin
    - https://www.ncbi.nlm.nih.gov/pubmed/27578330
    - Code in `./model/cipro.cpp`
- AUC:MIC ratio
    - The ciprofloxacin target AUC : MIC ratio is not reached in hospitalized 
      patients with the recommended dosing regimens
    - https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3555057

# Cipro PK: <grn>warm-up</grn>

```{r, eval=FALSE}
mod <- mread("cipro", "../../model")
```

- What are the parameters?
- What are the compartments?
- What is the model code?

# Cipro PK: <grn>infusion doses</grn>

- Simulate 400 mg as IV infusion over 1 hour

- Plot cipro concentration over 12 hours


# Cipro PK: <grn>infusion doses</grn>

- Simulate 400 mg as IV infusion over 1 hour

- Plot cipro concentration over 12 hours

<hr>

- Simulate 400 mg one day of a q12h dosing 

- Plot over 24 hours of dosing


# Cipro PK: <grn>covariates</grn>

Explore influence of patient weight, sex, and creatinine clearance on cipro PK

- Weight: 40 to 140 kg
- Creatinine clearance: 90, 60, 45, 30, 15 mL/min
- Sex: male / female
- Inputs: `idata_set`, `event` object
- Outputs: ciprofloxacin concentration, covariate values



# Cipro PK: <grn>AUC</grn>

From the Haeseker paper:

> Mean (+/- SD) age was 66 (+/-17) years, the mean clearance corrected for 
bodyweight was 0.24 l h-1 kg^1 <red>and the mean AUC was 49 mg l^1 h</red>.

Table 2 shows CrCL, CL, V, and AUC by total daily ciprofloxacin dose

Let's confirm the AUC result for each of the covariate groups in the 
previous step.

Use `PKPDmisc::auc_partial` to calculate AUC.

# Cipro PK: <grn>organ-specific exposure</grn>

>Profiles of unbound ciprofloxacin concentration in different tissues were 
predicted from the developed WB-PBPK model (Fig. 3). <blu>Kidney and lung were 
predicted to have higher exposures</blu> as compared to the other organs while 
muscle, brain and adipose were predicted to have relatively low exposures to 
ciprofloxacin.

Let's look at exposure in different organs

Use `./model/cipro_conc.cpp` model 

# Cipro PK: <grn>simulation with uncertainty</grn>


ciprofloxacin 400 mg IV over 2 hours

What is the distribution of AUC after the last dose on day 3 of q12h dosing?

Use `./model/cipro.cpp`

Use `./data/cipro_post.RDS`


# Cipro PK: <grn>AUC:MIC</grn>

Simulate the distribution of 24-hour AUC:MIC for

- MIC: 0.5
  - 200 mg IV q12h over 1 hour with CRCL = 30 ml/min
  - 400 mg IV q12h over 1 hour, normal renal function
  
- MIC: 1
  - 400 mg IV q12h over 1 hour 
  - 400 mg IV q8h  over 1 hour


Check progress on the second day of dosing



