---
title: "Probability of Technical Success - EPO IV/SC QW/TIW"
author: "Metrum Research Group"
---

```{r, message = FALSE}
source("../src/global.R")
source("../src/functions.R")
future::plan(future::multiprocess)
library(mrgsolve)
library(tidyverse)
library(future.apply)
Sys.setenv(R_FUTURE_FORK_ENABLE=TRUE)
set.seed(112)
```


__Population Pharmacokinetic and Pharmacodynamic Model- Based Comparability Assessment of a Recombinant Human Epoetin Alfa and the Biosimilar HX575__

- Xiaoyu Yan, MS, Philip J. Lowe, PhD, Martin Fink, PhD, Alexander Berghout, PhD, 
  Sigrid Balser, PhD, and Wojciech Krzyzanski, PhD

- J Clin Pharmacol. 2012 November ; 52(11): 1624–1644. 

- https://www.ncbi.nlm.nih.gov/pubmed/22162538


# Read in data ...
```{r}
post <- readRDS("../data/epo_post.RDS") %>% sample_n(nrow(.))

post <- select(post, contains("THETA"))

head(post)

dim(post)
```

# ... and the model
```{r}
mod <- mread_cache("epo", "../model") %>% zero_re()
see(mod)

```

Drop the initial `HGB` by a little bit
```{r}
mod <- param(mod,    THETA19 = mod$THETA19*0.8)
post <- mutate(post, THETA19 = THETA19*0.8)
```

# Weekly and tiw dosing
```{r}
qw <- ev(amt = 40000, ii = 168, addl = 3, rate = -2)

tiw <- ev_days(ev(amt = 7000, rate = -2), days="m,w,f", addl = 3)
tiw


qw <- filter(tiw, time==0) %>% mutate(amt = 40000)
qw
```

```{r}
data_sc <- bind_rows(tiw,qw) %>% mutate(ID = amt)
data_sc
```

# SC administration

- When subcuteneous administration, 40,000 IU weekly has similar efficacy
to 100 IU/kg TIW
- We're looking out to 4 weeks here
```{r}
mod %>% 
  mrgsim(data = data_sc, end = 672) %>%
  plot(EPOi + HGBi~.)
```

```{r}
data_sc
data_iv <- mutate(data_sc, cmt = 2, rate = 0)
data_iv
```

# IV administration

- But when we look at the TIW versus QW comparison with IV administration,
the once-weekly is less effective than three-times-weekly

```{r}
mod %>% 
  mrgsim(data = data_iv, end = 672) %>%
  plot(EPOi + HGBi~.)
```

# Probability of technical success

Let's look at the probability of technical success for the QW versus TIW
dosing in the IV case

Let's ramp this up for PTS

## Population data sets

TIW data
```{r}
iv_tiw <- ev_rep(tiw, ID = 1:150) %>% mutate(cmt = 2, rate = 0)
```

QW data
```{r}
iv_qw <- filter(iv_tiw, time==0) %>% mutate(amt = 40000, ID = ID + 10000)
```

If we bind this all together, we can simulate both regimens in one go
```{r}
data <- bind_rows(iv_tiw, iv_qw) %>% mutate(qw = as.integer(amt==40000))

head(data)
```

- What about simulating some variatility in Weight?


A simulation function

Arguments

- `i` replicate number
- `mod` the EPO model object
- `data` a template data set

```{r}
mod <- mread_cache("epo", "../model")
mod <- param(mod, THETA19 = mod$THETA19*0.8)

sim <- function(i, mod, data) {
  
  mod <- param(mod, slice(post,i))
  
  out <- mrgsim_d(mod, data = data, obsonly = TRUE,
                carry_out = "qw", end = -1, add = c(0,672), output="df")
  
  mutate(out, irep = i)
}
```


Test it out
```{r}
sim(2, mod, data) %>% head
```


## Simulate

- Remember to set a seed
- What about uncertainty in the random effect variances?

```{r}
set.seed(10020)
out <- future_lapply(
  seq(500),
  sim, mod, data
) %>% bind_rows
```


## Summarize

Our target is HGB > 10

```{r}
sum1 <- 
  out %>% 
  filter(time > 0) %>%
  group_by(irep,time,qw) %>%
  summarise(success = mean(HGBi >= 10), n = n())  %>%
  ungroup() %>%
  mutate(week = time/24/7)

sum1

ggplot(sum1, aes(x = success)) + geom_histogram(col="grey") + 
  facet_grid(week~qw) 
```

Our success criteria is at least 75% of patients hitting the target
```{r}
sum2 <- 
  sum1 %>%
  group_by(week,qw) %>% 
  summarise(PR = mean(success > 0.75))
```

The bottom line
```{r}
sum2
```

